---
title: "Big Mac"
author: "Nadezda Carr"
date: "3/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Get an estimated demand curve for Mig Macs

```{r}
BigMcdata = read.csv('BigMC.csv')
attach(BigMcdata)
```

plot the data

```{r}
plot(demand, price)

```

fit a demand line to these data

```{r}
priceone = 4.95
model1 = lm(price~demand)
summary(model1)
plot(demand, price)
abline(model1)
abline(h = priceone, col='red')
```
Price elasticity is a percent change in quantity demanded devided by the percent change in price

Marginal revenue of any product is the additional revenue for sales of one additional Big Mac.

Marginal revenue is related to price elasticity by

MR = price * (1 + elasticity)/elasticity

At MCDonalds MR = MC

E = slope of demand at price P * (price/quantity)

```{r}
slope = model1$coefficients[2]
intercept = model1$coefficients[1]
demanded = (priceone-intercept)/slope

E = slope*priceone/demanded

MR = priceone * ((1+E)/E)

print(paste('price =', priceone))
print(paste('demanded =',demanded))

print(paste('elasticity =',round(E,2)))
print(paste('MR = ', round(MR,2)))
```
Profit = price - cost = 4.5-MC

```{r}
profit = priceone - MR
print(paste('profit =', round(profit,2)))

```

